---
title: "plotly 2"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: readable
---

This is extra work for NOAA data.

```{r, include=FALSE}
library(tidyverse)
library(rnoaa)
library(plotly)
```

Because the data set is huge, we just choose one weather station to analyze. Randomly we choose station with id `USC00309072`

```{r}
noaa = 
  read.csv("./data/nynoaadat.csv") %>% 
  janitor::clean_names() %>% 
  filter(id == "USC00309072") %>% 
  separate(date, into = c("year", "month", "day"), sep = "-") %>% 
  mutate(
    year = as.numeric(year),
    month = as.numeric(month),
    day = as.numeric(day),
    month = month.name[month]
  )
```


## Scatterplot

First, we want to know that in this station, the relationship between minimum temperature (tenths of degrees C) (`tmin`) and snowfall (mm) (`snow`).

```{r, warning=FALSE, message=FALSE}
snow_temp = 
  noaa %>% 
  filter(!(snow == 0)) %>% 
  plot_ly(
    x = ~tmin, y = ~snow, type = "scatter", mode = "markers"
  )

snow_temp
```

## Boxplot

This boxplot show the precipitation distribution from 1995 to 2010. Because outliers will extremely influence our boxplot, I limit the `pcrp` range from 100 mm to 400 mm.

```{r}
year_prcp = 
  noaa %>%
  mutate(
    year = as.factor(year)
  ) %>% 
  group_by(year) %>% 
  filter(prcp %in% 100:400) %>% 
  filter(year %in% 1995:2010) %>% 
  plot_ly(
    x = ~year, y = ~prcp, type = "box"
  )

year_prcp
```

## Bar plot

This bar plot shows the mean precipitation (mm) between 1995 - 2010.

```{r}
aver_prcp = 
  noaa %>% 
  group_by(year) %>% 
  drop_na(prcp) %>% 
  summarize(mean_prcp = mean(prcp)) %>% 
  plot_ly(
    x = ~year, y = ~mean_prcp, type = "bar"
  )

aver_prcp
```

